\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue
}

\setlength{\headheight}{14.49998pt}
\addtolength{\topmargin}{-2.49998pt}

\title{\bf{Software Engineering Project}}
\author{\bf{DispatchNet:} \\ Alessio Zanon \\ Leonardo Tonetta \\ Luca Fiorini}
\date{\it{Requirements Analysis}}

\makeatletter
\renewcommand*{\numberline}[1]{\hb@xt@5em{#1\hfil}} 
\makeatother

\makeatletter
\NewExpandableDocumentCommand{\mynumbering}{m}{%
  \ExpandArgs{c}\@mynumbering{c@#1}%
}
\ExplSyntaxOn
\NewExpandableDocumentCommand{\@mynumbering}{m}
 {
  \int_case:nn { #1 }
   {
    {1}{O }
    {2}{FR }
    {3}{NFR }
    %...
   }
 }
\ExplSyntaxOff

\renewcommand{\thesection}{\mynumbering{section}}

\pagestyle{fancy}
\fancyhead[l]{DispatchNet}
\fancyhead[c]{Project TRE}
\fancyhead[r]{v0.5}
\fancyfoot[c]{\thepage}

\renewcommand\bf[1]{\textbf{#1}}
\renewcommand\it[1]{\textit{#1}}
\newcommand\un[1]{\underline{#1}}
\newcommand\hyl[1]{\hyperref[#1]{#1}}
\newcommand\subs[2]{\subsection{#1}\label{#2}}
\newcommand\ssubs[2]{\subsubsection{#1}\label{#2}}

\begin {document}
\maketitle

\newpage
\tableofcontents \label{Contents}

\section*{Readability notes}
\bf{Bold} words are system-important constructs. \newline
\un{Underlined} nouns are actors of the system. \newline
\it{Italic} words are special keywords to denote important limits of the project. \newline
\hyperref[Contents]{Hyperlinks} in reference to sections and subsections will be blue. \newline
\href{https:\\www.google.com}{Hyperlinks} to external web content will be in magenta.
\newpage

\addcontentsline{toc}{section}{Purpose}
\section*{Purpose}
This document describes the scope and the requirements of the Project "TRE", which implements a rail transport management system.

The purpose of this document is to: 
\begin{itemize}
	\item Specify the objectives.
	\item Identify the primary stakeholders.
	\item Define the functional and non-functional requirements.
\end{itemize}

\section{Objectives}

A major European rail infrastructure manager received an idea for a unified rail service scheduling and ticketing system, and has chosen us to prototype a trial run, over multiple regions in their network.\\

Thus, the project provides a platform that covers the needs of both \un{passengers} and \un{train companies}, as well as an underlying 
management system of any regional-sized rail network, which supports \un{network managers} in its administration. \\
It provides a set of functionalities which support the planning of train travel. The system lets \un{passengers} discover paths, view scheduling and manage tickets. On the other side, it lets \un{train companies} introduce train services and \un{network managers} administer the network.\\
The project coordinates the functionalities for each stakeholder into a solution that has been identified in an application accessible for the aforesaid users. \\

\noindent The main objectives of the project are:

\subs{Ticketing system}{O.1}
Subsystem which deals with tickets, from the search to the possible actions after the purchase. 
It includes basic operations that the \un{passenger} can perform, such as:
\begin{itemize}
	\item Viewing tickets details.
	\item Purchase.
	\item Accessing tickets history.
	\item Cancellation.
\end{itemize}

% \it{Boundary:} The project assumes the use of a third-party \un{payment gateway} system, implementing only a place-holder for a real 
% integration with it.

\subs{Route-finding}{O.2}
The system shall let \un{passengers} select a starting station, a destination station, and either a departure time or arrival time.\\
It computes and ranks possible \bf{routes} that best fit the user's request and permissions
(for example, not permitting cargo trains to \un{passengers}).\\
The user must be able to compare the options based on:
\begin{itemize}
    \item Departure and arrival times.
    \item Number of transfers.
    \item Possible transfer locations.
\end{itemize}

\subs{Virtual board}{O.3}
The system provides \un{passengers} access to departure and arrival boards for any station. It also shows intermediate stations and scheduled times for each 
individual train service.

\subs{Rail system modeling}{O.4}
The system provides a data-driven approach to rail network modelling, supporting an efficient administration of the infrastructure.\\
It shall support:
\begin{itemize}
    \item Management of the network by the \un{network manager}.
    \item Management of rolling stock by the \un{network manager}.
    \item Submission of a new service request by \un{train companies}.
    \item Review of a service request by the \un{network manager}.
\end{itemize}
\phantomsection
\addcontentsline{toc}{section}{Stakeholders}
\section*{Stakeholders}

\addcontentsline{toc}{subsection}{Internal}
\subsection*{Internal}

\addcontentsline{toc}{subsubsection}{Human}
\subsubsection*{Human}
\un{Network managers}, the product owner. They manage the rail network combining the availability of \un{train companies} with \un{passengers'} needs.\\
They are the primary stakeholders for making functional decisions.

\addcontentsline{toc}{subsection}{External}
\subsection*{External}

\addcontentsline{toc}{subsubsection}{Human}
\subsubsection*{Human}
\un{Passengers}, the main end users. They want to streamline their interactions with the train transport system, including:
\begin{itemize}
	\item Searching for routes and schedules.
	\item Analyzing departure/arrival boards as well as train information.
	\item Purchasing tickets.
\end{itemize}

\noindent\un{Train companies}, who provide the rolling stock. They request the introduction of services. They are also expected to provide information of trains they ask to be managed.

\noindent\un{Anonymous users}, who have not yet authenticated. They are considered as passengers with restricted access to functionalities that require authentication.

\addcontentsline{toc}{subsubsection}{Non-human}
\subsubsection*{Non-human}
\un{Payment gateway}, which provides the underlying payment methods.\\

% \it{Boundary:} The project will not provide actual transactions nor integration with any payment application.

\newpage

\section{Functional requirements}
\subs{Account classification}{FR.1}
The system shall classify between \un{anonymous user}, \un{passenger}, \un{train company} operator and \un{network manager}. 
The additional functionalities are described in 
\hyperref[Table1]{Requirement restrictions based on user classification}.

\subs{Account registration}{FR.2}
Following \hyl{FR.1}, in reference to \hyl{NFR.2}, the system must allow \un{anonymous users} to register. Data must 
satisfy \hyl{NFR.3}. Password must satisfy \hyl{NFR.4} and \hyl{NFR.5}.

\ssubs{Consent management}{FR.2.1}
Following \hyl{NFR.6}, in reference to \hyl{FR.2}, at registration the system must request the user's consent for personal 
data processing.

\ssubs{Account registration notification}{FR.2.2}
In reference to \hyl{FR.2}, after successful registration the system must notify the user as described at \hyl{NFR.9}.

\subs{Account deletion}{FR.3}
Following \hyl{NFR.1}, the system shall allow users to delete their accounts. Any other related data is also deleted.

\ssubs{Account deletion notification}{FR.3.1}
In reference to \hyl{FR.3}, after successful deletion the user is notified as described at \hyl{NFR.9}.

\subs{Data request management}{FR.4}
Following \hyl{NFR.7}, in reference to \hyl{NFR.2}, the system must provide users view of their stored information.

\subs{Account data change}{FR.5}
Following \hyl{NFR.8}, in reference to \hyl{NFR.2}, the system must allow users to change their data. New data must 
satisfy \hyl{NFR.3}.

\ssubs{Account data change notification}{FR.5.1}
In reference to \hyl{FR.5}, after a successful change operation the user is notified as described at \hyl{NFR.9}.

\subs{Password reset}{FR.6}
Following \hyl{NFR.8}, in reference to \hyl{NFR.2}, the system shall allow users to reset the password and change it (\hyl{NFR.9}). 
New password must satisfy \hyl{NFR.4} and \hyl{NFR.5}.

\subs{Login}{FR.7}
Following \hyl{FR.1}, the system must let users login using their username and password defined at registration (\hyl{FR.2}).

\it{Boundary:} The \un{network manager} has default account username "admin" and password "Password1234".

\subs{Logout}{FR.8}
Following \hyl{FR.1}, the system shall let logged in users log out, switching to the restricted \un{anonymous user's} 
functionalities. 

\subs{Tickets details display}{FR.9}
Following \hyl{O.1}, the system must allow \un{passengers} to view tickets. 

\subs{Tickets purchase}{FR.10}
Following \hyl{O.1}, the system must allow \un{passengers} to buy tickets.

\ssubs{Tickets purchase confirmation}{FR.10.1}
Following \hyl{O.1}, in reference to \hyl{FR.10}, the \un{passenger} must be asked for a final confirmation before purchase.

\ssubs{Tickets purchase notification}{FR.10.2}
Following \hyl{O.1}, in reference to \hyl{FR.10}, at the end of a purchase operation, the system must notify the \un{passenger} as 
described at \hyl{NFR.9}.

\subs{Tickets cancellation}{FR.11}
Following \hyl{O.1}, the system must allow the cancellation of purchased tickets. 

\ssubs{Tickets cancellation confirmation}{FR.11.1}
Following \hyl{O.1}, in reference to \hyl{FR.11} and \hyl{NFR.9}, the \un{passenger} must be asked for a final confirmation before 
cancellation.

\ssubs{Tickets cancellation notification}{FR.11.2}
Following \hyl{O.1}, in reference to \hyl{FR.11}, at the end of a cancellation operation, the system must notify the \un{passenger} as 
described at \hyl{NFR.9}.

\subs{Tickets history}{FR.12}
Following \hyl{O.1}, the system must allow \un{passengers} to view their tickets history, both purchased and cancelled.

\ssubs{Tickets classification}{FR.12.1}
Following \hyl{O.1}, in reference to \hyl{FR.12}, the tickets history must show whether a ticket is valid, expired, or 
cancelled.

\subs{Path search}{FR.13}
Following \hyl{O.2}, the system needs to be able to compute multiple paths between stations.

\ssubs{Path points}{FR.13.1}
Following \hyl{O.2}, extending \hyl{FR.13}, the \un{passenger} must be able to choose both the first and last stations of paths to be computed.

\ssubs{Path timing}{FR:13.2}
Following \hyl{O.2}, extending \hyl{FR.13}, the \un{passenger} shall be able to optionally specify a departure time and/or a latest 
arrival time. If neither is specified, the system must consider paths with departure times starting from the current time.

\subs{Path ranking}{FR.14}
Following \hyl{O.2}, in reference to \hyl{FR.13}, the system needs to rank the paths with a criteria selected by the \un{passenger} among a fixed list.

\ssubs{Ranking length}{FR.14.1}
Following \hyl{O.2}, in reference to \hyl{FR.14}, the system shall rank paths by prioritizing those with shortest travel time, and, secondarily, those with fewer intermediate stations.

\ssubs{Ranking deviation "Departure"}{FR.14.2}
Following \hyl{O.2}, in reference to \hyl{FR.14}, the system shall rank paths by prioritizing those whose first 
departure time is closest (but not earlier than) the user requested departure time.

\ssubs{Ranking deviation 2 "Arrival"}{FR.14.3}
Following \hyl{O.2}, in reference to \hyl{FR.14}, the system shall rank paths by prioritizing those whose last 
arrival time is closest (but not later than) the user requested departure time.

\ssubs{Ranking cost}{FR.14.4}
Following \hyl{O.2}, in reference to \hyl{FR.14}, the system shall rank paths by prioritizing those with lower total cost of 
tickets not already owned by the user.

\subs{Transfers}{FR.15}
Following \hyl{O.2}, in reference to \hyl{FR.13}, the system needs to compute transfer paths out of intersecting routes.

\subs{Segregation}{FR.16}
Following \hyl{O.2}, in reference to \hyl{FR.13}, the system must not consider train routes that pass by trains that the \un{passenger} is not allowed to purchase a ticket for.

\subs{Station display}{FR.17}
Following \hyl{O.3}, the system must provide departure and arrival times of all trains that pass through any station.

\subs{Train display}{FR.18}
Following \hyl{O.3}, the system must provide departure and arrival times of a train at all the stations on its schedule.

\subs{Path display}{FR.19}
The system must provide the board described at \hyl{FR.18} for each train in a given path, limited to the segments in which the train participates.

\subs{Creating a Service Request}{FR.20}
Following \hyl{O.4}, \un{companies} must be allowed to send the system a request for the introduction of a service.

\subs{Defining a Train Type}{FR.21}
Following \hyl{O.4}, in reference to  \hyl{FR.22}, the system must allow \un{companies} to register a train type to be used when defining a service.

\subs{Defining a Service Type}{FR.22}
Following \hyl{O.4}, in reference to \hyl{FR.20} and \hyl{FR.21}.  
The system must allow \un{companies} to define services and classes, as well as a pricing model for passenger trains.

\subs{Viewing the Network}{FR.23}
Following \hyl{O.3}, the system must allow users to access a map of the network.

\subs{Managing a Station}{FR.24}
Following \hyl{O.4}, the system must allow \un{network managers} to manage a station.

\ssubs{Registering a Station}{FR.24.1}
Following \hyl{O.4}, in reference to \hyl{FR.24}, the system must allow \un{network managers} to register a station.

\ssubs{Modifying a Station}{FR.24.2}
Following \hyl{O.4}, in reference to \hyl{FR.24}, the system must allow \un{network managers} to modify any existing station.

\ssubs{Deleting a Station}{FR.24.3}
Following \hyl{O.4}, in reference to \hyl{FR.24}, the system must allow \un{network managers} to delete any existing station.

\subs{Managing a Line}{FR.25}
Following \hyl{O.4}, the system must allow \un{network managers} to manage a line.

\ssubs{Registering a Line}{FR.25.1}
Following \hyl{O.4}, in reference to \hyl{FR.25}, the system must allow \un{network managers} to register a line.  

\ssubs{Modifying a Line}{FR.25.2}
Following \hyl{O.4}, in reference to \hyl{FR.25}, the system must allow \un{network managers} to modify any existing line.  

\ssubs{Deleting a Line}{FR.25.3}
Following \hyl{O.4}, in reference to \hyl{FR.25}, the system must allow \un{network managers} to delete any existing line.

\subs{Managing a Junction}{FR.26}
Following \hyl{O.4}, the system must allow \un{network managers} to manage a junction.

\ssubs{Registering a Junction}{FR.26.1}
Following \hyl{O.4}, in reference to \hyl{FR.26}, the system must allow \un{network managers} to register a junction.  

\ssubs{Modifying a Junction}{FR.26.2}
Following \hyl{O.4}, in reference to \hyl{FR.26}, the system must allow \un{network managers} to modify any existing junction.  

\ssubs{Deleting a Junction}{FR.26.3}
Following \hyl{O.4}, in reference to \hyl{FR.26}, the system must allow \un{network managers} to delete any existing junction.  

\subs{Automated Service Integrity Checks}{FR.27}
Following \hyl{O.4}, the system must autonomously perform integrity checks on proposed services.
Integrity checks are defined by the following.

\ssubs{Single Track Line Availability Check}{FR.27.1}
Following \hyl{O.4}, specifying \hyl{FR.27}, the system must ensure that no two services are scheduled to traverse a single track line in opposite directions at the same time.

\ssubs{Platform Availability Check}{FR.27.2}
Following \hyl{O.4}, specifying \hyl{FR.27}, the system must ensure that no two services are scheduled to stop at the same platform at the same time.

\ssubs{Track-side Systems Compatibility Check}{FR.27.3}
Following \hyl{O.4}, specifying \hyl{FR.27}, the system must ensure that all trains used for a service are compatible with the signaling and electrification systems installed on the traversed infrastructure.

\ssubs{Track Geometry Check}{FR.27.4}
Following \hyl{O.4}, specifying \hyl{FR.27}, the system must ensure that all trains used for a service are compatible with both the loading and track gauges of the infrastructure they traverse.

\subs{Displaying Integrity Check Results}{FR.28}
Following \hyl{O.4}, extending \hyl{FR.27}, the system must provide the integrity check results.

\subs{Service Request Review}{FR.29}
Following \hyl{O.4}, in reference to \hyl{FR.20}, the system must allow the \un{network manager} to review requests.

\ssubs{Service Request approval}{FR.29.1}
Following \hyl{O.4}, in reference to \hyl{FR.20} and \hyl{FR.29}, the \un{network manager} must be able to approve a service request, notifying (\hyl{NFR.9}) the \un{train company} that submitted the request.

\ssubs{Service Request amendment}{FR.29.2}
Following \hyl{O.4}, in reference to \hyl{FR.20} and \hyl{FR.29}, the system must allow the \un{network manager} to send back an amended version of the request for 
the \un{train company} to review, notifying (\hyl{NFR.9}) them.

\ssubs{Service Request denial}{FR.29.3}
Following \hyl{O.4}, in reference to \hyl{FR.20} and \hyl{FR.29}, the system must allow the \un{network manager} to deny a service request, notifying (\hyl{NFR.9}) the \un{train company} that submitted the request.

\addcontentsline{toc}{subsection}{Requirement restrictions based on user classification}
\subsection*{Requirement restrictions based on user classification}\label{Table1}
\begin{center}
	\begin{tabular}{c|c c c c }
	\hline
	\bf{Requirement} &Anonymous &Passenger &Train company &Manager \\
	\hline
	\begin{tabular}{@{}c@{}}
	\bf{FR.1}\\
    \bf{FR.6}\\
	\bf{FR.23}	
	\end{tabular} &Yes &Yes &Yes &Yes \\
	\hline
	\begin{tabular}{@{}c@{}}
	\bf{FR.2}\\
	\bf{FR.7} 
	\end{tabular} &Yes & & & \\
	\hline
	\bf{FR.3-5} & &Yes &Yes & \\
	\hline
	\bf{FR.8} & &Yes &Yes &Yes \\
	\hline
	\begin{tabular}{@{}c@{}}
	\bf{FR.9}\\
	\bf{FR.13-19} 
	\end{tabular} &Yes &Yes & & \\
	\hline
	\bf{FR.10-12} & &Yes & & \\
	\hline
	\bf{FR.20-22} & & &Yes & \\
	\hline
	\begin{tabular}{@{}c@{}}
	\bf{FR.24-28}
	\end{tabular} & & & &Yes \\
	\hline
	\bf{FR.29} & & &Self &Self \\
	\hline
	\end{tabular}
\end{center}
\it{Caption:}\\
Self: access to resources regarding only the personal part of the functionality.

\newpage

\section{Non-functional requirements}

\subs{Data Protection Regulation}{NFR.1}
\un{External requirement - Legislative requirement} \\

\noindent The system must respect the \href{https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=CELEX%3A02016R0679-20160504&qid=1532348683434}
{Regulation (EU) 2016/679} on the protection of natural persons with regard to the processing of personal data. 
With special attention to:
\begin{itemize}
	\item[\bf{Art. 5}] Principles relating to processing of personal data, ensuring ethical processing.
	\item[\bf{Art. 6, 7}] Lawfulness of processing and Conditions for consent, both concerning consent for the processing 
	of personal data.
	\item[\bf{Art. 13}] Information to be provided where personal data are collected from the data subject, 
	i.e. providing information of the controller of the processing.
	\item[\bf{Art. 15}] Right of access by the data subject, i.e. users must be able to see their stored information.
	\item[\bf{Art. 16}] Right to rectification, i.e. users must be able to change their information.
	\item[\bf{Art. 17}] Right to erasure (‘right to be forgotten’).
	\item[\bf{Art. 32}] Security of processing.
\end{itemize}

\subs{Account data}{NFR.2}
\un{Product requirement - Security requirement} \\

\noindent Following \hyl{FR.1} and \hyl{NFR.1}, in reference to \hyl{FR.2}, user accounts must include username, email and 
password.

\subs{Account data details}{NFR.3}
\un{Product requirement - Security requirement} \\

\noindent Following \hyl{NFR.1} and \hyl{NFR.2}, account data must satisfy the following:
\begin{itemize}
	\item The username must be unique.
	\item The email must be unique.
\end{itemize}

\subs{Password security}{NFR.4}
\un{Product requirement - Security requirement} \\

\noindent Following \hyl{NFR.1} and \hyl{NFR.2}, in reference to \hyl{FR.2.1}, the password must be at least 8 characters, 
with at least one upper and one lowercase letters and one digit.

\subs{Typo prevention}{NFR.5}
\un{Product requirement - Security requirement} \\

\noindent When a password is chosen or modified, the system must take prevention to mitigate typos: it must require the password to be typed twice and only accepted if both match.

\subs{Consent for personal data processing}{NFR.6}
\un{External requirement - Legislative requirement} \\

\noindent Following \hyl{NFR.1}, the system must comply with the GDPR for data processing consent.

\subs{Request of processed data}{NFR.7}
\un{External requirement - Legislative requirement} \\

\noindent Following \hyl{NFR.1}, the system must comply with the GDPR for accessing processed data.

\subs{Rectification of processed data}{NFR.8}
\un{External requirement - Legislative requirement} \\

\noindent Following \hyl{NFR.1}, the system must comply with the GDPR for the right of rectification.

\subs{Email notification}{NFR.9}
\un{Product requirement - Usability requirement} \\

\noindent In order to notify users, the system shall use the email service, using the one inserted at registration (\hyl{FR.2}).

\subs{Station-train display switching}{NFR.10}
Users must be able to switch with a single prompt/input between the following

\ssubs{Station to train display}{NFR.10.1}
\un{Product requirement - Usability requirement} \\

\noindent A station's display and a train's display passing 
through that station.

\ssubs{Train to station display}{NFR.10.2}
\un{Product requirement - Usability requirement} \\

\noindent A train's display and a station's display in its 
schedule.

\subs{Station-path searching switching}{NFR.11}
Users must be able to switch with a single prompt/inpu between the following.

\ssubs{Station "from" path}{NFR.11.1}
\un{Product requirement - Usability requirement} \\

\noindent A station's display and the route-finding 
procedure with the station automatically set as the path's start.

\ssubs{Station "to" path}{NFR.11.2}
\un{Product requirement - Usability Requirement} \\

\noindent A station's display and the route-finding 
procedure with the station automatically set as the destination.

\subs{Path list to path list}{NFR.12}
\un{Product requirement - Usability requirement} \\

\noindent Users must be able to switch from a list of paths according to a ranking option to another, in no more 
steps/inputs than the ones required to select a different ranking. 

\subs{Ranking non-choice}{NFR.13}
\un{Product requirement - Usability requirement} \\

\noindent The system shall default to the ranking described at \hyl{FR.14.1} until a different ranking choice is given by the user.

\end {document}
