\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	colorlinks=true,
	linkcolor=blue
}

\setlength{\headheight}{14.49998pt}
\addtolength{\topmargin}{-2.49998pt}

\title{\bf{Software Engineering Project}}
\author{\bf{DispatchNet:} \\ Alessio Zanon \\ Leonardo Tonetta \\ Luca Fiorini}
\date{\it{Requirements Analysis}}

\makeatletter
\renewcommand*{\numberline}[1]{\hb@xt@5em{#1\hfil}} 
\makeatother

\makeatletter
\NewExpandableDocumentCommand{\mynumbering}{m}{%
  \ExpandArgs{c}\@mynumbering{c@#1}%
}
\ExplSyntaxOn
\NewExpandableDocumentCommand{\@mynumbering}{m}
 {
  \int_case:nn { #1 }
   {
    {1}{O }
    {2}{FR }
    {3}{NFR }
    %...
   }
 }
\ExplSyntaxOff

\renewcommand{\thesection}{\mynumbering{section}}

\pagestyle{fancy}
\fancyhead[l]{DispatchNet}
\fancyhead[c]{Project TRE}
\fancyhead[r]{v1.1}
\fancyfoot[c]{\thepage}

\renewcommand\bf[1]{\textbf{#1}}
\renewcommand\it[1]{\textit{#1}}
\newcommand\un[1]{\underline{#1}}
\newcommand\hyl[1]{\hyperref[#1]{#1}}
\newcommand\subs[2]{\subsection{#1}\label{#2}}
\newcommand\ssubs[2]{\subsubsection{#1}\label{#2}}

\begin {document}
\maketitle

\newpage
\tableofcontents \label{Contents}

\section*{Readability notes}
\bf{Bold} words are system-important constructs. \newline
\un{Underlined} nouns are actors of the system. \newline
\it{Italic} words are special keywords to denote important limits of the project. \newline
\hyperref[Contents]{Hyperlinks} in reference to sections and subsections will be blue. \newline
\href{https:\\www.google.com}{Hyperlinks} to external web content will be in magenta. \newline
\textcolor{green}{Green text} is text added or modified for D2.

\newpage

\addcontentsline{toc}{section}{Purpose}
\section*{Purpose}
This document describes the scope and the requirements of the Project "TRE", which implements a rail transport management system.

The purpose of this document is to: 
\begin{itemize}
	\item Specify the objectives.
	\item Identify the primary stakeholders.
	\item Define the functional and non-functional requirements.
\end{itemize}

\input{D1_BodyText.tex}

\end {document}
